Mainstreaming Scientific Racism

### 2022-11-08 talk/talk.qmd
race science def'n slide

<!-- 
## PF and MQ as a race science echo chamber?

- Empirical, text-mining approach
- Identify Pioneer-funded researchers
- Identify journals that published their work
- Analyze all articles published in those journals, 1960-2010

\
 -->

@@

<!--
## Some definitions

scientific racism
 ~ (purportedly) justifying racial inequality and colonialism by appealing to the epistemic authority of science

- Ex: genotype clustering studies [@RosenbergGeneticStructureHuman2002] or polygenic scores for educational attainment [@HardenGeneticAssociationsMathematics2019] 
can be wide-sense race science without being narrow-sense race science [@CarlsonQuantifyingContextualizingImpact2020; WillsAreClustersRaces2017]

- This talk will focus on narrow-sense race science
-->

@@

>>>>

@@

@@

## Some definitions {visibility="uncounted"}

scientific racism
 ~ (purportedly) justifying racial inequality and colonialism by appealing to the epistemic authority of science\
   [compare @LewontinBourgeoisIdeologyOrigins1982]

Ex: genotype clustering studies [@RosenbergGeneticStructureHuman2002] or polygenic scores for educational attainment [@HardenGeneticAssociationsMathematics2019] 
can be wide-sense race science without being narrow-sense race science [@WillsAreClustersRaces2017; @CarlsonQuantifyingContextualizingImpact2020]
